Discon analysis

### 2018-11-25 analysis/01_analysis.Rmd
speaker change experiment

files <- dir("../../adult_600_visual/sandbox-results/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../adult_600_visual/sandbox-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

@@

ggplot(plot1,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(~distribution, 
             labeller = as_labeller(c(`c(5, 1, 0)` = "Distribution\n(5-1-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```
# How does the last item seen affect the object chosen in the anaphora case? 
```{r last item}
plot2 <- data %>%
  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
  mutate(trackLast = ifelse(lastInputCat == target1, "yes", "no")) %>%
  group_by (distribution, workerid) %>%
  summarise (lastInput = mean(same_lastInput),
             n = n()) %>% 
  multi_boot_standard(col = "lastInput")

>>>>

files <- dir("../../adult_600_mumble/production-results/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../adult_600_mumble/production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

@@

ggplot(plot1,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(~distribution, 
             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```
# How does the last item seen affect the object chosen in the anaphora case? 
```{r last item}
plot2 <- data %>%
  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
  mutate(trackLast = ifelse(lastInputCat == target1, "yes", "no")) %>%
  group_by (distribution, workerid) %>%
  summarise (lastInput = mean(same_lastInput),
             n = n()) %>% 
  multi_boot_standard(col = "lastInput")
